Case study validations of automatic bullet matching

### 2018-10-02 index.Rmd
updated citation

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. (Set 173 was originally published as Hamby set 44. This has been corrected now.)

Here, we are considering three validation sets:
\begin{itemize}
\item {\bf Hamby set 44} 
Hamby set 44 is one set of the Hamby study \citep{hamby}. Each Hamby set  consists of a total of 35 bullets fired through ten consecutively manufactured barrels of Rugers P85. Each set consists of 20 known bullets (two from each of the ten barrels) and 15 questioned bullets of unknown origin. Note that all Hamby sets are closed sets, i.e. all questioned bullets are fired through one of the ten barrels. The ammunition used for this set were 9 mm Luger 115 Grain Full Metal Jacket  from the Winchester Ammunition Company.
\item {\bf Phoenix PD}
Tylor Klep from Phoenix PD provided sets of known and unknown bullets: the set of known bullets consists of three test fires (B1, B2, B3) from each of eight different barrels (A9, C8, F6, L5, M2, P7, R3, U10). Ten unknown bullets were provided (B, E, H, J, K N, Q, T, Y, Z). Land engraved areas for each of the six lands of each bullet were scanned by Bill Henderson (Sensofar).
\item {\bf Houston FSI}
This study was set up by Melissa Nally and Kasi Kirksey from FSI Houston. Three test sets based on ten consecutively rifled Ruger LCP barrels (A, B, C, D, E, F, G, H, I, J) and three other, non-consecutively rifled Ruger LCP barrels (R1, R2, R3). Each test set consists of three test fires each from five consecutively rifled barrels. Additionally, ten unknowns bullets are provided for each kit. The ammunition used in both test fires and the unknowns were Remington UMC 9mm Luger Full Metal Jackets.
\end{itemize}

>>>>

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44. This has been rectified now.

Here, we are considering three validation sets: 
\begin{itemize}
\item {\bf Hamby set 44} 
Hamby set 44 is one set of the Hamby study \citep{hamby}. Each Hamby set  consists of a total of 35 bullets fired through ten consecutively manufactured barrels of Rugers P85. Each set consists of 20 known bullets (two from each of the ten barrels) and 15 questioned bullets of unknown origin. Note that all Hamby sets are closed sets, i.e. all questioned bullets are fired through one of the ten barrels. The ammunition used for this set were 9 mm Luger 115 Grain Full Metal Jacket  from the Winchester Ammunition Company.
\item {\bf Phoenix PD}
Tylor Klep from Phoenix PD provided sets of known test fires and questioned bullets: the set of known bullets consists of three test fires (B1, B2, B3) from each of eight different barrels (A9, C8, F6, L5, M2, P7, R3, U10). Ten questioned bullets were provided (B, E, H, J, K N, Q, T, Y, Z). This set is an open set, i.e.\ it is not known in advance whether all (or any) of the questioned bullets are fired from the known barrels.
Land engraved areas for each of the six lands of each bullet were scanned by Bill Henderson (Sensofar).
\item {\bf Houston FSI}
This study was set up by Melissa Nally and Kasi Kirksey from FSI Houston. Three test sets based on ten consecutively rifled Ruger LCP barrels (A, B, C, D, E, F, G, H, I, J) and three other, non-consecutively rifled Ruger LCP barrels (R1, R2, R3). Each test set consists of three test fires each from five consecutively rifled barrels. Additionally, ten unknowns bullets are provided for each kit. The ammunition used in both test fires and the unknowns were Remington UMC 9mm Luger Full Metal Jackets.
\end{itemize}
